Calendar-based graphics for visualizing people's daily schedules

### 2017-08-27 main.Rmd
fixed some jss formatting issues

---
author:
  - name: Earo Wang
    affiliation: Monash University
    address: >
      Department of Econometrics and Business Statistics,
      Monash University, VIC 3800
      Australia
    email: \email{earo.wang@monash.edu}
  - name: Dianne Cook
    affiliation: Monash University
    address: >
      Department of Econometrics and Business Statistics,
      Monash University, VIC 3800
      Australia
    email: \email{dicook@monash.edu}
  - name: Rob J Hyndman
    affiliation: Monash University
    address: >
      Department of Econometrics and Business Statistics,
      Monash University, VIC 3800
      Australia
    email: \email{rob.hyndman@monash.edu}
title:
  formatted: "Calendar-based graphics for visualizing people's daily schedules"
  plain: "Calendar-based graphics for visualizing people's daily schedules"
abstract: >
  This paper describes a \code{frame\_calendar} function that organizes and displays temporal data, collected on sub-daily resolution, into a calendar layout. Calendars are broadly used in society to display temporal information, and events. The \code{frame\_calendar} uses linear algebra on the date  variable to create the layout. It utilizes the grammar of graphics to create the plots inside each cell, and thus synchronizes neatly with \pkg{ggplot2} graphics. The motivating application is studying pedestrian behavior in Melbourne, Australia, based on counts which are captured at hourly intervals by sensors scattered around the city. Faceting by the usual features such as day and month, was insufficient to examine the behavior. Making displays on a monthly calendar format helps to understand pedestrian patterns relative to  events such as work days, weekends, holidays, and special events. The layout algorithm has several format options and variations. It is implemented in the R package \pkg{sugrrants}.

keywords:
  # at least one keyword must be supplied
  formatted: [data visualization, statistical graphics, time series, R package, grammar of graphics]
  plain:     [data visualization, statistical graphics, time series, R package, grammar of graphics]
preamble: >
  \usepackage{amsmath}
output: 
  bookdown::pdf_book:
    base_format: rticles::jss_article
  citation_package: biblatex
bibliography: ["references.bib", "packages.bib"]
---

@@

By default, grids are laid out horizontally. This can be transposed by setting the \code{dir} parameter to \code{"v"}, in which case $i$ and $j$ are swapped in the equation \eqref{eq:grid}. This can be useful for creating  calendar layouts for countries where vertical layout is the convention.

>>>>

---
author:
  - name: Earo Wang
    affiliation: Monash University
    address: >
      Department of Econometrics and Business Statistics,
      Monash University, VIC 3800
      Australia
    email: \email{earo.wang@monash.edu}
  - name: Dianne Cook
    affiliation: Monash University
    address: >
      Department of Econometrics and Business Statistics,
      Monash University, VIC 3800
      Australia
    email: \email{dicook@monash.edu}
  - name: Rob J Hyndman
    affiliation: Monash University
    address: >
      Department of Econometrics and Business Statistics,
      Monash University, VIC 3800
      Australia
    email: \email{rob.hyndman@monash.edu}
title:
  formatted: "Calendar-based graphics for visualizing people's daily schedules"
  plain: "Calendar-based graphics for visualizing people's daily schedules"
abstract: >
  This paper describes a \code{frame\_calendar} function that organizes and displays temporal data, collected on sub-daily resolution, into a calendar layout. Calendars are broadly used in society to display temporal information, and events. The \code{frame\_calendar} uses linear algebra on the date  variable to create the layout. It utilizes the grammar of graphics to create the plots inside each cell, and thus synchronizes neatly with \pkg{ggplot2} graphics. The motivating application is studying pedestrian behavior in Melbourne, Australia, based on counts which are captured at hourly intervals by sensors scattered around the city. Faceting by the usual features such as day and month, was insufficient to examine the behavior. Making displays on a monthly calendar format helps to understand pedestrian patterns relative to  events such as work days, weekends, holidays, and special events. The layout algorithm has several format options and variations. It is implemented in the \proglang{R} package \pkg{sugrrants}.

keywords:
  # at least one keyword must be supplied
  formatted: [data visualization, statistical graphics, time series, grammar of graphics, "\\proglang{R}"]
  plain:     [data visualization, statistical graphics, time series, R package, grammar of graphics]
preamble: >
  \usepackage{amsmath}
output: 
  bookdown::pdf_book:
    base_format: rticles::jss_article
  citation_package: biblatex
bibliography: ["references.bib", "packages.bib"]
---

@@

By default, grids are laid out horizontally. This can be transposed by setting the \code{dir} parameter to \code{"v"}, in which case $i$ and $j$ are swapped in the Equation \ref{eq:grid}. This can be useful for creating  calendar layouts for countries where vertical layout is the convention.

### 2017-08-27 main.tex
fixed some jss formatting issues

\Abstract{
This paper describes a \code{frame\_calendar} function that organizes
and displays temporal data, collected on sub-daily resolution, into a
calendar layout. Calendars are broadly used in society to display
temporal information, and events. The \code{frame\_calendar} uses linear
algebra on the date variable to create the layout. It utilizes the
grammar of graphics to create the plots inside each cell, and thus
synchronizes neatly with \pkg{ggplot2} graphics. The motivating
application is studying pedestrian behavior in Melbourne, Australia,
based on counts which are captured at hourly intervals by sensors
scattered around the city. Faceting by the usual features such as day
and month, was insufficient to examine the behavior. Making displays on
a monthly calendar format helps to understand pedestrian patterns
relative to events such as work days, weekends, holidays, and special
events. The layout algorithm has several format options and variations.
It is implemented in the R package \pkg{sugrrants}.
}

\Keywords{data visualization, statistical graphics, time series, R package, grammar of graphics}
\Plainkeywords{data visualization, statistical graphics, time series, R package, grammar of graphics}

@@

\usepackage{amsthm}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{definition}
\newtheorem{example}{Example}[section]
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\begin{document}

@@

By default, grids are laid out horizontally. This can be transposed by
setting the \code{dir} parameter to \code{"v"}, in which case \(i\) and
\(j\) are swapped in the equation \eqref{eq:grid}. This can be useful
for creating calendar layouts for countries where vertical layout is the
convention.

>>>>

\Abstract{
This paper describes a \code{frame\_calendar} function that organizes
and displays temporal data, collected on sub-daily resolution, into a
calendar layout. Calendars are broadly used in society to display
temporal information, and events. The \code{frame\_calendar} uses linear
algebra on the date variable to create the layout. It utilizes the
grammar of graphics to create the plots inside each cell, and thus
synchronizes neatly with \pkg{ggplot2} graphics. The motivating
application is studying pedestrian behavior in Melbourne, Australia,
based on counts which are captured at hourly intervals by sensors
scattered around the city. Faceting by the usual features such as day
and month, was insufficient to examine the behavior. Making displays on
a monthly calendar format helps to understand pedestrian patterns
relative to events such as work days, weekends, holidays, and special
events. The layout algorithm has several format options and variations.
It is implemented in the \proglang{R} package \pkg{sugrrants}.
}

\Keywords{data visualization, statistical graphics, time series, grammar of graphics, \proglang{R}}
\Plainkeywords{data visualization, statistical graphics, time series, R package, grammar of graphics}

@@

\usepackage{amsthm}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{definition}
\newtheorem{example}{Example}[section]
\theoremstyle{definition}
\newtheorem{exercise}{Exercise}[section]
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\begin{document}

@@

By default, grids are laid out horizontally. This can be transposed by
setting the \code{dir} parameter to \code{"v"}, in which case \(i\) and
\(j\) are swapped in the Equation \ref{eq:grid}. This can be useful for
creating calendar layouts for countries where vertical layout is the
convention.
